INTELLIGENT SYSTEMS

### 2021-04-15 papers/paper_8.tex
finish 8.3.1

>>>>

\subsection{METHODS}
\subsubsection{Multi Stream Deep Similarity Learning Networks}
A mulit-stream similarity learning network is used in this paper. In the 
proposed framework there are various data streams (Fig. \ref{fig:EMDSLT}):
\begin{enumerate}
    \item Template Stream: the target template defined in the beginning frame;
    \item Searching Stream: the search region;
    \item Background Stream: background patches that sample around the target 
    in the beginning frame.
\end{enumerate}

\subsubsection{Template-Searching-Background Loss}
